---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r, echo = FALSE}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(embed)
library(tidymodels)
th <- theme_minimal() +
    theme(
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "#f7f7f7"),
        panel.border = element_rect(fill = NA, color = "#0c0c0c"),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        strip.text = element_text(size = 16),
        legend.position = "bottom"
    )
theme_set(th)
```

[Single-Cell Genomics]  In this problem, we will apply UMAP to a
[dataset](https://uwmadison.box.com/shared/static/ai539s30rjsw5ke4vxbjrxjaiihq7edk.csv)
of Peripheral Blood Mononuclear Cells (PBMC) released by 10X Genomics. The first
column, `cell_tag`, gives an identifier for each cell in the dataset. All other
columns are molecules that were detected in that cell. For example, CD74 is a
molecule often found on the surface of T-cells.
    
a. Define a tidymodels `recipe` that specifies that UMAP should be performed
with the parameters `learn_rate = 0.1` and `neighbors = 5`. There is no need to
normalize these data, as they have been normalized in advance using methods
tailored to single-cell genomics data.

```{r}
pbmc <- read_csv("https://uwmadison.box.com/shared/static/ai539s30rjsw5ke4vxbjrxjaiihq7edk.csv")
pbmc
# setup recipe
# specify which are metadata/numerical
# specify to use UMAP


umap_rec <- recipe(~ ., data = pbmc) |>
    update_role(cell_tag, new_role = "id") |>
    step_umap(all_predictors(), neighbors = 5, learn_rate = 0.1)

umap_prep <- prep(umap_rec)
```

b. Compute the UMAP embeddings across cells. Color points in by their value of
the GNLY molecule.

```{r}
embeddings <- bake(umap_prep, new_data = NULL) |>
    left_join(pbmc)

library(scico)
ggplot(embeddings) +
    geom_point(aes(UMAP1, UMAP2, col = GNLY)) +
    scale_color_scico(palette = "batlow")

```

```{r}

umap_rec <- recipe(~ ., data = pbmc) |>
    update_role(cell_tag, new_role = "id")


n_neighbor <- round(seq(5, 50, length.out = 5))
embeddings <- list()
for (i in seq_along(n_neighbor)) {
    embeddings[[paste0("k_", n_neighbor[i])]] <- umap_rec |>
        step_umap(all_predictors(), neighbors = n_neighbor[i], learn_rate = 0.1) |>
        prep() |>
        bake(new_data = NULL)
}

bind_rows(embeddings, .id = "neighbors") |>
    left_join(pbmc) |>
    mutate(neighbors = as.integer(str_extract(neighbors, "[0-9]+"))) |>
    ggplot() +
    geom_point(aes(UMAP1, UMAP2, col = GNLY)) +
    scale_color_scico(palette = "batlow") +
    facet_wrap(~ neighbors)

```