---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r}
library(tidyverse)
library(tidygraph)
library(ggraph)
```

1. [Movie Genres] How do movie genres relate to one another? Is romance + comedy
a more common combination than fantasy + adventure? We will use the dataset
[here](https://github.com/krisrs1128/stat436_s24/raw/main/data/movie_links.csv)
to answer these questions, using a node-link diagram inspired by (but much
simpler than) the [film flowers](https://observablehq.com/@sxywu/introduction-to-svg-and-d3-js) project
by Shirley Wu.

a. Build a `tbl_graph` containing the movies and their links.

```{r}
edges <- read_csv("https://github.com/krisrs1128/stat436_s24/raw/main/data/movie_links.csv")
genres <- read_csv("https://github.com/krisrs1128/stat436_s24/raw/main/data/genres.csv")

edges
genres

G <- tbl_graph(edges = edges) |>
    mutate(
        is_genre = ifelse(name %in% genres$genre, "Yes", "No"),
        short_name = sub(":.*", "", name)
        )


```

b. Create a node-link diagram to represent the connections between movies and
their genres.

```{r}
ggraph(G, layout = "kk") +
    geom_edge_link(colour = "#d3d3d3", alpha = 0.6, width = 0.5) +
    geom_node_text(aes(label = short_name, col = is_genre, size = is_genre)) +
    scale_color_manual(values = c("#BF4545", "#225C73")) +
    scale_size_discrete(range = c(3.5, 5)) +
    theme_void() +
    theme(legend.position = "none")


ggraph(G, layout = "matrix") +
    geom_edge_tile(mirror = TRUE) +
    #geom_node_text(aes(label = short_name)) +
    geom_node_text(aes(label = short_name), angle = 90, y = -0.5, hjust = 1) +
    geom_node_text(aes(label = short_name), angle = 0, x = -0.5, hjust = 1) +
    scale_y_discrete(expand = c(0, 80, 0, 0)) +
    scale_x_discrete(expand = c(0, 80, 0, 0)) +
    theme_void()
```

c. A list of all the genres in this network is available
[here](https://github.com/krisrs1128/stat992_f23/blob/main/activities/week9/genres.csv).
Design a strategy to distinguish between genres and movies, and justify your
choice of visual encodings. _Hint: Mutate the nodes in the `tbl_graph`._


1. [UK Energy Flow] We will visualize how energy is produced and consumed in the
United Kingdom, using a [dataset](https://github.com/krisrs1128/stat436_s24/raw/main/data/energy.csv) from the UK's Department of Energy and Climate
Change. Nodes and edges are used to classify types of activity that produce or
consume energy. For example, the edge

```
Wind    Electricity grid    289 
```

means that 289 KwH produced by wind power were sent to the country's electricity grid.

a. Build a `tbl_graph` from the provided edges. Ensure that the resulting
graph object has directed edges.

```{r}
edges <- read_csv("https://github.com/krisrs1128/stat436_s24/raw/main/data/energy.csv")
edges

G <- tbl_graph(edges = edges)
G
```

b. Use `ggraph` to visualize the flow of energy across nodes in this
network. Ensure nodes are annotated.

```{r}
ggraph(G, layout = "kk") +
    geom_edge_link(
        aes(linewidth = value), 
        colour = "#d3d3d3", alpha = 0.6,
        arrow = arrow(),
        end_cap = circle(4, "mm")
        ) +
    geom_node_label(aes(label = name)) +
    theme_void()

```

c. Experiment with several layouts. Which do you find most useful? Is there
an alternative layout you would prefer? Explain your reasoning.



For labeling in adjacency matrices, see: https://github.com/krisrs1128/stat436_s24/blob/81d1f39b5e39088f8bbba32594f8b2bb73408153/notes/2024-12-27-week08-03.Rmd