---
title: "Untitled"
output: 
  html_document:
    theme: cerulean
    css: styles.css
date: "`r Sys.Date()`"
---

```{r}
#knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```


[Plant Growth Experiment] This problem will give you practice with tidying a
dataset so that it can be easily visualized. The data describe the height of
several plants measured every 7 days. The plants have been treated with
different amounts of a growth stimulant. The first few rows are printed below --
`height.x` denotes the height of the plant on day `x`.

```{r}
library(tidyverse)
plants <- read_csv("https://uwmadison.box.com/shared/static/qg9gwk2ldjdtcmmmiropcunf34ddonya.csv")
plants
```

a. Propose an alternative arrangement of rows and columns that conforms to the
tidy data principle.

b. Implement your proposed arrangement from part (a).

```{r}
plants_long <- plants |>
    pivot_longer(starts_with("height")) |>
    mutate(
        day = as.integer(str_extract(name, "[0-9]+"))
    )

plants_long
```

c. Using the dataset from (b), design and implement a visualization showing the
growth of the plants over time according to different treatments.

```{r}
theme_set(theme_classic())
ggplot(plants_long) +
    geom_line(
        aes(
            day, value,
            col = treatment,
            group = interaction(plantid, treatment)
        )
    ) +
    facet_wrap(~ treatment)
```